Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-10 article/article.Rmd
Commit 2024-09-10 13:11

<!-- END -->

>>>>

```{r  echo=FALSE, fig.cap="Example of Colar constant of $1367\\,\\text{W}/\\text{m}^{2}$. The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.", fig.pos='H'}
knitr::include_graphics("../images/P-example-day-12.png")
```
<!-- END -->
